Second Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE2): Submission, Peer-Review and Sorting Process, and Results

### 2015-02-06 WSSSPE2_report/WSSSPE2_review_report.tex
initial commit of WSSSPE2 report - just with pre-workshop report content for now

\title[]{Second Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE2): Submission, Peer-Review, and Sorting Process, and Results}

>>>>

\title[]{Second Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE2): Submission, Peer-Review and Sorting Process, and Results}
